\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}
\setlength{\footskip}{4.08003pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Tighter margins for one-page fit
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]
\pdfgentounicode=1
% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small #1
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubheadingCollege}[6]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=2pt, partopsep=0pt, parsep=0pt, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newenvironment{tightItemList}{\begin{itemize}[topsep=2pt, partopsep=0pt, parsep=1pt, itemsep=1pt]}{\end{itemize}\vspace{-6pt}}
\begin{document}
\begin{center}
\textbf{\Huge Nikhil Singh} \\ \vspace{1pt}
\small +91 9560324262 $|$ \href{mailto:nik.singh710@gmail.com}{\underline{nik.singh710@gmail.com}} $|$
\href{https://linkedin.com/in/niksingh710}{\underline{linkedin.com/in/niksingh710}} $|$
\href{https://github.com/niksingh710}{\underline{github.com/niksingh710}}
\end{center}
%-----------SKILLS-----------
\vspace{-20pt}
\section{Skills}
\vspace{-6pt}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: C/C++, Rust, Go, Haskell, Java, Python, Bash, Nix} \\
\textbf{Systems}{: Linux (NixOS), low-latency systems, debugging, performance optimization} \\
\textbf{Infrastructure}{: NixOS/Flakes, Docker, CI/CD (Jenkins, GitHub Actions), GCP} \\
\textbf{Developer Tools}{: Git, Neovim, Tmux, QEMU, SSH} \\
\textbf{Backend Frameworks}{: Django, FastAPI, Flask, Actix Web (Rust), Servant (Haskell)} \\
\textbf{Datastores \& Messaging}{: MySQL, MongoDB, Redis, Kafka} \\
\textbf{Engineering Focus}{: Backend systems, distributed workflows, reproducible infrastructure, performance-sensitive software}
}}
\end{itemize}
\end{multicols}

\vspace{-8pt}
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Product Engineer}{Jun 2025 -- Present}
{Juspay Technologies}{Bengaluru, KA}
\resumeItemListStart
\resumeItem{Owned and maintained critical backend services, participating in design reviews, on-call debugging, and production incident resolution.}
\resumeItem{Designed failure-handling, retry, and reconciliation mechanisms for distributed payment workflows.}
\resumeItem{Designed and operated event-driven backend services handling high-volume UPI payment traffic with high availability.}
\resumeItem{Reduced request latency and load using Redis caching and internal signaling in high-concurrency flows.}
\resumeItem{Added monitoring and alerting for payment services to improve visibility and speed up incident resolution.}
\resumeItem{Maintained deterministic production builds and deployments using Nix for multi-language services.}
\resumeItemListEnd
\resumeSubheading
{Researcher — Systems \& Software Engineering}{May 2023 -- May 2025}
{Gautam Buddha University}{Greater Noida, UP}
\resumeItemListStart
\resumeItem{Applied research outcomes to practical system design, emphasizing reproducibility, modularity, and long-term maintainability.}
\resumeItem{Authored an IEEE-published paper on modular, lazy-evaluated NixOS configurations for reproducible operating system management
(\href{https://ieeexplore.ieee.org/document/10991248}{IEEE Xplore}).}
\resumeItem{Developed reusable Nix flake-based system configurations using disko, impermanence, and home-manager to enable hardware-agnostic, ephemeral deployments.}
\resumeItem{Co-authored an IEEE-published study on ML-based heavy rainfall prediction for the Northern Himalayan region
(\href{https://ieeexplore.ieee.org/document/10990912}{IEEE Xplore}).}
\resumeItemListEnd
\resumeSubheading
{Other Professional Experience}{2023 -- 2024}
{Multiple Roles}{Remote \& Greater Noida}
\resumeItemListStart
\resumeItem{Built backend services and automation workflows as a Software Developer Intern, working with REST APIs and Linux-based systems.}
\resumeItem{Mentored and led hands-on workshops on Git and reproducible development environments for 100+ participants.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-14pt}
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Custom Android Build System} $|$ \emph{CI/CD, Linux, AOSP}}{2019 -- 2022}
\begin{tightItemList}
\resumeItem{Built and automated Android ROM build and OTA pipelines using Jenkins for multiple devices.}
\resumeItem{Debugged AOSP and kernel-level issues, managing patch workflows for stable multi-device releases.}
\resumeItem{Made architectural trade-offs between performance, maintainability, and reproducibility, documenting decisions for long-term use.}
\end{tightItemList}

\resumeProjectHeading
{\textbf{Open Source Contributions}}{Ongoing}
\begin{tightItemList}
\resumeItem{Maintainer of Tmux Minimal Status (240+ stars), focusing on performance, reliability, and minimal design.}
\resumeItem{Reviewed issues and pull requests, guiding contributors and maintaining project quality standards.}
\resumeItem{Contributed to Hyprwm, AUR, and Nixpkgs, primarily on tooling improvements and system reliability.}
\end{tightItemList}

\resumeProjectHeading
{\textbf{Ndots \& Nvix}}{2024 -- Present}
\begin{tightItemList}
\resumeItem{Designed modular, declarative NixOS configurations using flakes for reproducible and portable Linux systems.}
\resumeItem{Built a modular Neovim distribution with an optimized plugin system and fast startup performance.}
\resumeItem{Made design decisions balancing reproducibility, performance, and ease of maintenance across systems.}
\end{tightItemList}

\resumeSubHeadingListEnd
\vspace{-14pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheadingCollege
{Gautam Buddha University}{Greater Noida, UP}
{Master of Technology in Software Engineering \textbf{(CGPA: 8.83)}}{Aug. 2023 -- May 2025}
{Bachelor of Technology in Computer Science Engineering}{Aug. 2020 -- Aug. 2023}
\resumeSubHeadingListEnd
\end{document}
